---
title: "Coursera Developing Data Products Week 4 Project"
author: "V Pawar"
date: "November 23, 2018"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This is an app developed using R Studion shiny package.  The app uses diamonds dataset available in R and then interactively parses to give desired information to the user.

-User selects cuts for the dimaond.
     Quality of the cuts are: Fair, Good, Very Good, Premium, Ideal
     
-User selects color for the diamond
    Diamond color are :J (worst) to D (best)
    
-USer selects clarity for the diamond
    Diamond clarity is defined as: I1 (worst), SI2, SI1, VS2, VS1, VVS2, VVS1, IF (best)
    
-The other factors length(x), width(y), and depth(z) are not evaluated in the app

## Diamonds dataset

```{r}
require(ggplot2)
suppressMessages({library(ggplot2)})
diamonds[1:10]
```

## Example of Plot from the App

```{r }
suppressMessages({library(ggplot2)})
diamondsub <- subset(diamonds, cut == "Ideal" & color == "D" & clarity == "IF")
ggplot(data = diamondsub, aes(x = carat, y = price)) + geom_point(color='red', size= 4)+geom_smooth ()+xlab("Carat")+ylab("Price")+theme_bw()

```

## Link to the App and code

-App:
    https://pawarvd.shinyapps.io/myappweek4project/

-Github:
    https://github.com/pawarvd/Developing-Data-Products



